Boundary Types

### 2014-12-19 sematics/boundary/boundary.tex
updates from meeting

\begin{mathpar}
\infer {\btyw i {\rm int}\rmunit} {\cdot} \and
\infer {\btyw b {\rm bool}\rmunit} {\cdot} \and
\infer {\btyw {(e_1,e_2)} {A \times B} {\tau_1 \times \tau_2}} 
	{\btyw {e_1} A {\tau_1} 
	&\btyw {e_2} B {\tau_2}} \and
\infer {\btyw {\pio~e} A \tau} 
	{\btyw {e} {A \times B} {\tau}} \and
\infer {\btyw {\pit~e} B \tau} 
	{\btyw {e} {A \times B} {\tau}} \and
\infer {\btyo {\next~e} B \tau} 
	{\btyt {e} {A \times B} {\tau}} \and
\infer {\btyt {\prev~e} B \tau} 
	{\btyo {e} {A \times B} {\tau}} \and
\infer {\btyt {\pause~e} \rmint \tau} 
	{\btyo e \rmint {\tau \times \rmint}}
\end{mathpar}

@@

\section{Adding Functions (But Not Ifs)}

>>>>

\begin{mathpar}
\infer {\btyw i {\rm int}\rmunit} {\cdot} \and
\infer {\btyw b {\rm bool}\rmunit} {\cdot} \and
\infer {\btyw {(e_1,e_2)} {A \times B} {\tau_1 \times \tau_2}} 
	{\btyw {e_1} A {\tau_1} 
	&\btyw {e_2} B {\tau_2}} \and
\infer {\btyw {\pio~e} A \tau} 
	{\btyw {e} {A \times B} {\tau}} \and
\infer {\btyw {\pit~e} B \tau} 
	{\btyw {e} {A \times B} {\tau}} \and
\infer {\btyo {\next~e} {\fut A} \tau} 
	{\btyt {e} A {\tau}} \and
\infer {\btyt {\prev~e} A \tau} 
	{\btyo {e} {\fut A} {\tau}} \and
\infer {\btyt {\pause~e} \rmint {\tau \times \rmint}} 
	{\btyo e \rmint \tau}
\end{mathpar}

@@

\section{Adding Just Functions}

Lets now take a different stab at this, by adding functions to our straight-line code,
but leaving \texttt{if}s out for now.
Again, lets consider an example:
\[
L1 := (\lam x \rmint {\next\{5\}})
\]
The boundary type of $L1$ is obviously unit, right?
After all, lambdas are values, and values have unit boundary.
So then what about this example:
\[
L2 := (\lam x \rmint {\next\{\pause\{x\}+1\}})
\]
I'd like to think it's the same story.
But what if we apply a value to these functions?
Consider
\[
(\lam x \rmint {\next\{5\}})~3
\]
versus
\[
(\lam x \rmint {\next\{\pause\{x\}+1\}})~3
\]
The boundary type of the first expression should still be unit 
(even after substitution it has no $\pause$s),
but the bound type of the second expression should definitely be int.

There's a problem here: $L1$ and $L2$ had the same boundary type before application, but different ones after.
This suggests that if we want the boundary type to be a compositional property (rather than global),
then we'll need to keep track of more information.

We do this by making a distinction between the {\em internal} boundary of an expression,
and its {\em external} boundary.  
$L1$ and $L2$ have the same external boundary, namely unit,
but they have different internal boundaries.  
In particular, the interal boundary of $L1$ should be int (or isomorphic to it), 
whereas the internal boundary of $L2$ should be unit.
